---
title: "The Impact of Corona Curfews on the Prices of Airbnb Listing in Amsterdam"
author: "Tayfun Ozcan, Jeroen Maagdenberg, Sam van de Ven and Quinten de Putter"
output:
  html_document:
    theme: journal
  pdf_document: default
---  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
  
```{r, echo = FALSE}
library(readr)
library(kableExtra)
library(modelsummary)
library(knitr)
```

In this project, we examine the impact of Corona curfews on the prices of Airbnb listings in Amsterdam. We use the data from [Inside Airbnb](http://insideairbnb.com/amsterdam/).

*Research question: Did the curfew affect the prices of Airbnb listings? Zooming in on Amsterdam*

### The following things are examined in this project:

  - Determining the effect of the curfew on the income of landlords.  
  - Effects of the neighbourhood on the Airbnb listing price.   
  - Effects of the host status on the Airbnb listing price.  

## Data

### Data Collection
First, we downloaded the file from [Inside Airbnb](http://insideairbnb.com/amsterdam/) from the period August 2020 till August 2021. The data is downloaded from the Airbnb website and is stored in Google Drive. 

### Data Processing

After downloading the datafiles were combined into one large dataset, we removed excessive variables, ordered the data,
changed variable types and added dummy variables.

### Variables

The dataset we use for the analysis is "gen/temp/Curfew_Amsterdam.csv" which consist of the following variables:

#### ID
Numeric Variable, every listing has it's own ID 

#### Date
Date Variable, information when data point was created

#### Host ID
Numeric Variable, every host has it's own ID

#### Host_is_superhost
Logical Variable, TRUE if host is registered as super host

#### Neighbourhood
Factor Variable, the neighbourhood in which the listing is located

#### Price
Numeric Variable, price of listing per night in American dollar

#### Dummy Variables: Curfew, Curfew 21:00, Curfew:22:00
Dummy Variable, 1 or a 0 depending on the government regulation that month.



### Summary Curfew_Amsterdam
```{r, echo=FALSE, message=FALSE, warning=FALSE}
Curfew_Amsterdam <- read_csv("../gen/temp/Curfew_Amsterdam.csv")
summary(Curfew_Amsterdam)
```


### Figure 1 - Price development during curfew regulations


```{r, echo = FALSE, fig.align='center', out.height='500px',out.width='500px'}
knitr::include_graphics(path = '../gen/paper/avgprice.pdf')
```

### Figure 2 - Price development during curfew whether host is superhost or not 

```{r, echo = FALSE, fig.align = 'center', out.height='500px',out.width='500px'}
include_graphics('../gen/paper/price_superhost.pdf')
```


### Table 1 - Linear Regression models
```{r prices, echo=FALSE, results="asis", message=FALSE, warning=FALSE}
library(stargazer)
Curfew_Amsterdam <- Curfew_Amsterdam <- read_csv("../gen/temp/Curfew_Amsterdam.csv")
m1log <- lm(log1p(price) ~ 1 + curfew + host_is_superhost, data = Curfew_Amsterdam)
m2log <- lm(log1p(price) ~ 1 + curfew + curfew_2200 + host_is_superhost, data = Curfew_Amsterdam)
m3log <- lm(log1p(price) ~ 1 + curfew + curfew_2200 + host_is_superhost + neighbourhood, data = Curfew_Amsterdam)

stargazer(m1log, m2log, m3log,
          title = "Impact curfew on Airbnb in Amsterdam",
          dep.var.caption = "DV: Price of listing",
          notes.label = "Significance levels",
          covariate.labels = c(
            "Curfew",
            "Curfew 22:00",
            "Host is Superhost",
            "Bijlmer Oost",
            "Bos en Lommer",
            "Buitenveldert Zuidas",
            "Centrum Oost",
            "Centrum West",
            "De Aker Nieuwe Sloten",
            "De Baarsjes Oud West",
            "De Pijp Rivierenbuurt",
            "Gaasperdam Driemond",
            "Geuzenveld Slotermeer",
            "IJburg Zeeburgereiland",
            "Noord Oost",
            "Noord West",
            "Oostelijk Havengebied Indische Buurt",
            "Osdorp",
            "Oud Noord",
            "Oud Oost",
            "Slotervaart",
            "Watergraafsmeer",
            "Westerpark",
            "Zuid",
            "Constant"),
          type = 'html')
```


## Results
Looking at figure 1, a remarkable result is that the listing prices in Amsterdam were at their lowest during the curfew months (January 2021 – April 2021) for the period of this research (August 2020 – August 2021). In addition, towards the end of the curfew, the prices slowly started to increase. 

Another interesting result is that the listings with a superhost have a price lower than listing without a superhost (figure 2). However, a larger increase in the prices of listings with a superhost than listings without a superhost was noticed in figure 2. Because of this, the prices are almost the same. Also, in table 1 it can be read that being a superhost is not very beneficial, it leads to listing prices being 8.8% lower compared to listings from hosts that are not superhosts during the Covid-19 pandemic. 

Reading table 1 it becomes clear that the curfew has a significant effect on the Airbnb listing prices in Amsterdam. Because the dependent variable (price) is written as a logarithmic function, it can be concluded that introducing the curfew resulted in a -1.5% price drop for the listings in Amsterdam. The introduction of the later curfew offsets this by 1%.

The impact of each neighbourhood can be found in table 1. Here it can be read that the effect of almost all the neighbourhood is greater than the curfew.

