---
title: "The Impact of Corona Curfews on the Prices of Airbnb Listing in Amsterdam"
author: "Tayfun Ozcan, Jeroen Maagdenberg, Sam van de Ven and Quinten de Putter"
output:
  html_document:
    theme: journal
---  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
  
```{r, echo = FALSE}
library(readr)
library(kableExtra)
library(modelsummary)
library(knitr)
```

In this project we examine the impact of Corona curfews on the prices of Airbnb listings in Amsterdam. We use the data from [Inside Airbnb](http://insideairbnb.com/amsterdam/).

*Research question: Did the curfew affect the prices of Airbnb listings? Zooming in on Amsterdam*

### The following things are examined in this project:

  Determining the effect of the curfew on the income of landlords.  
  Effects of the neighbourhood on the Airbnb listing price.   
  Effects of the host status on the Airbnb listing price.  

## Data

### Data Collection
First we downloaded the file from [Inside Airbnb](http://insideairbnb.com/amsterdam/) from the period August 2020 till August 2021. The data is downloaded from the Airbnb website and is stored in a Google Drive. 

### Data Processing

After downloading the datafiles were combined into one large dataset, we removed excessive variables, ordered the data,
changed variable types and added dummy variables.

### Variables

The dataset we use for the analysis is "gen/temp/Curfew_Amsterdam.csv" consist of the following variables:

#### ID
Numeric Variable, every listing has it's own ID 

#### Date
Date Variable, information when data point was created

#### Host ID
Numeric Variable, every host has it's own ID

#### Host_is_superhost
Logical Variable, TRUE if host is registered as super host

#### Neighbourhood
Factor Variable, the neighbourhood in which the listing is located

#### Price
Numeric Variable, price of listing per night in american dollar

#### Dummy Variables: Curfew, Curfew 21:00, Curfew:22:00
Dummy Variable, 1 or a 0 depending on the government regulation that month.



### Summary Curfew_Amsterdam
```{r, echo=FALSE, message=FALSE, warning=FALSE}
Curfew_Amsterdam <- read_csv("../gen/temp/Curfew_Amsterdam.csv")
summary(Curfew_Amsterdam)
```


### Figure 1 - Price development during curfew regulations


```{r, echo = FALSE, fig.align='center', out.height='40%'}
knitr::include_graphics(path = '../gen/paper/avgprice.pdf',)
```

### Figure 2 - Price development during  if host is superhost or not 

```{r, echo = FALSE, fig.align = 'center'}
include_graphics('../gen/paper/price_superhost.pdf')
```


### Table 1 - Linear Regression models
```{r prices, echo=FALSE, results="asis", message=FALSE, warning=FALSE}
library(stargazer)
Curfew_Amsterdam <- Curfew_Amsterdam <- read_csv("../gen/temp/Curfew_Amsterdam.csv")
m1log <- lm(log1p(price) ~ 1 + curfew + host_is_superhost, data = Curfew_Amsterdam)
m2log <- lm(log1p(price) ~ 1 + curfew + curfew_2200 + host_is_superhost, data = Curfew_Amsterdam)
m3log <-lm(log1p(price) ~ 1 + curfew + curfew_2200 + host_is_superhost + neighbourhood, data = Curfew_Amsterdam)

stargazer(m1log, m2log, m3log,
          title = "Impact curfew on Airbnb in Amsterdam",
          dep.var.caption = "DV: Price of listing",
          notes.label = "Significance levels",
          covariate.labels = c(
            "Curfew",
            "Curfew 22:00",
            "Host is Superhost",
            "Bijlmer Oost",
            "Bos en Lommer",
            "Buitenveldert Zuidas",
            "Centrum Oost",
            "Centrum West",
            "De Aker Nieuw Sloten",
            "De Baarsjes Oud West",
            "De Pijp Rivierenbuurt",
            "Gaasperdam Driemond",
            "Geuzenveld Slotermeer",
            "IJburg Zeeburgereiland",
            "Noord Oost",
            "Noord West",
            "Oostelijk Havengebied Indische Buurt",
            "Osdorp",
            "Oud Noord",
            "Oud Oost",
            "Slotervaart",
            "Watergraafsmeer",
            "Westerpark",
            "Zuid",
            "Constant"),
          type = 'html')
```


## Conclusion
In table 1 can be seen that the three variables that are examined have significant effects on the price of the Airbnb listing in Amsterdam. It can be concluded that the curfew had a negative impact on the price. One thing that stands out is that being a superhost during the Covid-19 pandemic resulted in a negative effect on price, which is interesting. As expected, neighbourhoods do have an effect.
